Schramm-Loewner evolution in tricritical Ising model

### 2013-06-05 AffineLieAlgebras/Simons/tricritical-ising-sle.tex
Minor changes,  calculations in Maxima added

Bolzmann weights are given by the expression
\begin{equation}
  \label{eq:5}
  W\left.\left(
    \begin{array}{cc}
      d & c\\
      a & b
    \end{array}\right| u \right)
= s_1 (-u)\delta_{ac} + \frac{s_0 (u) \psi_a^{1/2}
  \psi_c^{1/2}}{\psi_b} \delta_{bd},
\end{equation}
where
  \begin{equation}
    \label{eq:6}
    s_r(u)=\frac{\sin(r\lambda+u)}{\sin\lambda},\quad \frac{\lambda}{\pi}\not\in\mathbb{Z}.
%%      \left.s_r(u)\right|_{\frac{\lambda}{\pi}\in \mathbb{Z}} =
%%      \lim_{\lambda'\to \lambda} \frac{\sin(r \lambda'
%%        +(\lambda'-\lambda)u)}{\sin \lambda'}
  \end{equation}
We are interested in the case $A_4$, so $\lambda=0.62831853071796$ and
isotropic case $u=\lambda/2$. Conformal point is
$u=\xi_1=\xi_2=\lambda/2$. Then we have
$s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda}$.

>>>>

Bolzmann weights are given by the expression
\begin{equation}
  \label{eq:5}
  W\left.\left(
    \begin{array}{cc}
      d & c\\
      a & b
    \end{array}\right| u \right)
= s_1 (-u)\delta_{ac} + \frac{s_0 (u) \psi_a^{1/2}
  \psi_c^{1/2}}{\psi_b} \delta_{bd},
\end{equation}
where
  \begin{equation}
    \label{eq:6}
    s_r(u)=\frac{\sin(r\lambda+u)}{\sin\lambda},\quad \frac{\lambda}{\pi}\not\in\mathbb{Z}.
%%      \left.s_r(u)\right|_{\frac{\lambda}{\pi}\in \mathbb{Z}} =
%%      \lim_{\lambda'\to \lambda} \frac{\sin(r \lambda'
%%        +(\lambda'-\lambda)u)}{\sin \lambda'}
  \end{equation}
We are interested in the case $A_4$, so we have
$2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
$\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.
The isotropic case $u=\lambda/2$ with boundary parameters
$u=\xi_1=\xi_2=\lambda/2$ corresponds to the  conformal point. Then we have
$s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda/2}$.
